---
title: "Customer Support on Twitter Analysis"
author: "Taha Ababou"
format: html
---

Code attribution - originally in Python: **Stuart Axelbrooke · 7y ago**
<https://www.kaggle.com/code/soaxelbrooke/customer-sentiment-by-brand>


## Introduction

This report analyzes customer support interactions on Twitter, focusing on identifying the first inbound messages from customers and their responses from companies. Additionally, we will analyze customer sentiment by brand.

## Load Packages

```{r setup, include=FALSE}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidytext)
library(textdata)
library(sentimentr)
library(tidyr)
```

## Load Data

```{r}
# Load the dataset
tweets_original <- read.csv('../data/customer-support-on-twitter/twcs/twcs.csv')
str(tweets_original)
```
## Pooling

### No Pooling

For no pooling, split the dataset by author_id so that each subset contains data for a single author. This will allow you to analyze each author independently.

```{r}
# Load necessary packages
library(dplyr)

# Split the data by author_id
no_pooling_data <- split(tweets, tweets$author_id)

# Example: Access data for a specific author
no_pooling_data[["sprintcare"]]


```

### Partial Pooling

For partial pooling, you can use a mixed-effects model with author_id as a random effect. This will create estimates for each author that are influenced by the overall distribution.

```{r}
# Load the lme4 package for mixed-effects modeling
library(lme4)

# Fit a partial pooling model
# Assuming `response` is the outcome variable you want to model
# Replace 'response' with the name of your outcome variable
partial_pooling_model <- lmer(response ~ (1 | author_id), data = tweets)

# View model summary
summary(partial_pooling_model)

```


### Complete Pooling

For complete pooling, you ignore author_id and fit a model to the entire dataset as if it were a single group.

```{r}
# Fit a complete pooling model
# Assuming `response` is the outcome variable you want to model
# Replace 'response' with the name of your outcome variable
complete_pooling_model <- lm(text ~ 1, data = tweets)

# View model summary
summary(complete_pooling_model)


```

## Data Processing

Convert the `inbound` column to logical format and filter the data to identify the first inbound customer messages that are not replies to previous tweets.

```{r}
# Convert the 'inbound' column to logical type
tweets$inbound <- tweets$inbound == "True"

# Pick only inbound tweets that aren't in reply to anything
first_inbound <- tweets %>%
  filter(is.na(in_response_to_tweet_id) & inbound)
cat("Found", nrow(first_inbound), "first inbound messages.\n")

# Merge in all tweets in response
inbounds_and_outbounds <- first_inbound %>%
  inner_join(tweets, by = c("tweet_id" = "in_response_to_tweet_id")) %>%
  filter(inbound.y == FALSE)
cat("Found", nrow(inbounds_and_outbounds), "responses from companies.\n")
```

## Customer Sentiment by Brand

This section identifies the top 20 brands by support volume and finds the average sentiment for inbound customer requests to gauge customer sentiment.

```{r}
# Adjust based on the actual column name, using `text.x` if available
text_column <- if ("text.x" %in% colnames(inbounds_and_outbounds)) {
  "text.x"
} else if ("text" %in% colnames(inbounds_and_outbounds)) {
  "text"
} else {
  stop("Text column not found in the merged data")
}

# Convert the selected text column to character
inbounds_and_outbounds[[text_column]] <- as.character(inbounds_and_outbounds[[text_column]])

# Load AFINN sentiment lexicon for sentiment analysis
sentiments <- get_sentiments("afinn")

# Tokenize and perform sentiment analysis on the identified text column
sentiment_data <- inbounds_and_outbounds %>%
  unnest_tokens(word, !!sym(text_column)) %>%
  inner_join(sentiments, by = "word") %>%
  group_by(tweet_id, author_id.y) %>%
  summarize(inbound_sentiment = sum(value, na.rm = TRUE))
```

```{r}
# Identify top 20 brands by volume
top_support_providers <- sentiment_data %>%
  count(author_id.y, sort = TRUE) %>%
  top_n(20, n) %>%
  pull(author_id.y)

head(top_support_providers)

```


```{r}
# Load data.table package
library(data.table)

# Convert `sentiment_data` to a data.table
setDT(sentiment_data)

# Calculate the volume for each brand and order by descending count
brand_volume <- sentiment_data[, .N, by = author_id.y][order(-N)]

# Select only the top 20 brands by volume
top_20_brands <- head(brand_volume, 20)

# Convert back to `data.frame` for ggplot2
top_20_brands <- as.data.frame(top_20_brands)

# Plot Top 20 Brands by Volume
library(ggplot2)
ggplot(top_20_brands, aes(x = reorder(author_id.y, N), y = N)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Top 20 Brands by Volume", x = "Brand", y = "Volume")

```

```{r}
# Load data.table package
library(data.table)

# Convert `sentiment_data` to a data.table
setDT(sentiment_data)

# Calculate average sentiment for each brand in `top_support_providers`
sentiment_summary <- sentiment_data[author_id.y %in% top_support_providers, 
                                    .(avg_sentiment = mean(inbound_sentiment, na.rm = TRUE)), 
                                    by = author_id.y][order(avg_sentiment)]

# Select the top 20 brands with the most positive sentiment (highest avg_sentiment)
top_20_positive <- tail(sentiment_summary, 20)

# Select the worst 20 brands with the most negative sentiment (lowest avg_sentiment)
worst_20_negative <- head(sentiment_summary, 20)

# Convert both to data.frames for ggplot2
top_20_positive <- as.data.frame(top_20_positive)
worst_20_negative <- as.data.frame(worst_20_negative)

# Plot Top 20 Positive Brands by Sentiment
library(ggplot2)
ggplot(top_20_positive, aes(x = reorder(author_id.y, avg_sentiment), y = avg_sentiment)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Brands by Positive Sentiment", x = "Brand", y = "Average Sentiment")

# Plot Worst 20 Negative Brands by Sentiment
ggplot(worst_20_negative, aes(x = reorder(author_id.y, avg_sentiment), y = avg_sentiment)) +
  geom_bar(stat = "identity", fill = "red") +
  coord_flip() +
  labs(title = "Worst 20 Brands by Negative Sentiment", x = "Brand", y = "Average Sentiment")

```

## Case Study: Apple Support Volume & Sentiment

We analyze \@AppleSupport tweets around the launch of the iPhone X to observe trends in customer sentiment and volume over time.

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidytext)
library(textdata)

# Ensure 'created_at.x' is in POSIXct date-time format
inbounds_and_outbounds <- inbounds_and_outbounds %>%
  mutate(created_at.x = as.POSIXct(created_at.x, format = "%a %b %d %H:%M:%S %z %Y", tz = "UTC"))

# Filter for tweets from @AppleSupport after October 7, 2017
apple_tweets <- inbounds_and_outbounds %>%
  filter(author_id.y == "AppleSupport" & created_at.x >= as.POSIXct("2017-10-07", tz = "UTC"))

# Convert text to character if needed
apple_tweets$text.x <- as.character(apple_tweets$text.x)

# Load the AFINN lexicon for sentiment analysis
afinn <- get_sentiments("afinn")

# Calculate sentiment for each tweet
apple_tweets <- apple_tweets %>%
  unnest_tokens(word, text.x) %>%
  inner_join(afinn, by = "word") %>%
  group_by(tweet_id, created_at.x) %>%
  summarize(inbound_sentiment = mean(value, na.rm = TRUE)) %>%
  ungroup()

# Calculate daily average sentiment and tweet volume
daily_summary <- apple_tweets %>%
  mutate(date = as.Date(created_at.x)) %>%
  group_by(date) %>%
  summarize(
    avg_sentiment = mean(inbound_sentiment, na.rm = TRUE),
    tweet_volume = n()
  ) %>%
  ungroup()

# Plot Daily Tweet Volume
ggplot(daily_summary, aes(x = date, y = tweet_volume)) +
  geom_col(fill = "lightblue") +
  labs(
    title = "@AppleSupport Daily Inbound Tweet Volume Post iPhone X Launch",
    x = "Date",
    y = "Number of Inbound Tweets"
  ) +
  theme_minimal()

# Plot Daily Average Sentiment
ggplot(daily_summary, aes(x = date, y = avg_sentiment)) +
  geom_line(color = "red") +
  geom_smooth(method = "loess", color = "blue", fill = "lightblue", se = TRUE) +
  labs(
    title = "@AppleSupport Daily Average Sentiment Post iPhone X Launch",
    x = "Date",
    y = "Average Sentiment"
  ) +
  theme_minimal()


```

## Conclusion

This analysis identifies initial customer support requests and corresponding responses from companies on Twitter. Additionally, it provides sentiment insights for the top 20 brands and examines sentiment trends over time for Apple Support around the iPhone X launch. This data can be used for further sentiment analysis, response optimization, and other insights for customer support improvement.
