### Customer Support by Brand

An analysis of customer support interactions by specific brands was
conducted to identify brands with the most negative and positive
customer sentiments. This examination provides a clearer understanding
of brand-specific support performance and areas for improvement.

```{r include=FALSE, echo=FALSE}
# Calculate average sentiment by brand
sentiment_summary <- tweets %>%
  group_by(author_id) %>%
  summarise(avg_sentiment = mean(sentiment_score, na.rm = TRUE)) %>%
  arrange(avg_sentiment)

# Select top 20 positive and top 20 negative brands
top_20_positive <- sentiment_summary %>%
  top_n(20, avg_sentiment)

worst_20_negative <- sentiment_summary %>%
  top_n(-20, avg_sentiment)
```

#### Top 20 Brands by Positive Sentiment

```{r include=FALSE, echo=FALSE}
# Plot Top 20 Positive Brands
ggplot(top_20_positive, aes(x = reorder(author_id, avg_sentiment), y = avg_sentiment)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Brands by Positive Sentiment", x = "Brand", y = "Average Sentiment") +
  theme_minimal()

# [Graph: Top 20 Brands by Positive Sentiment]
```

The top 20 brands with the highest average positive sentiment scores
were identified. These brands demonstrate effective customer support
strategies that foster positive customer experiences.

#### Worst 20 Brands by Negative Sentiment

```{r include=FALSE, echo=FALSE}
# Plot Worst 20 Negative Brands
ggplot(worst_20_negative, aes(x = reorder(author_id, avg_sentiment), y = avg_sentiment)) +
  geom_bar(stat = "identity", fill = "red") +
  coord_flip() +
  labs(title = "Worst 20 Brands by Negative Sentiment", x = "Brand", y = "Average Sentiment") +
  theme_minimal()

# [Graph: Worst 20 Brands by Negative Sentiment]
```

The worst 20 brands with the lowest average negative sentiment scores
were identified. These brands may need to address underlying issues to
improve customer satisfaction and support effectiveness.