---
title: "Customer Support on Twitter Analysis"
author: "Taha Ababou"
format: html
---

## Introduction

This report analyzes customer support interactions on Twitter, focusing on identifying the first inbound messages from customers and their responses from companies.

## Load Packages

```{r}
# Load necessary libraries
library(dplyr)

# Load the dataset
tweets <- read.csv('../data/customer-support-on-twitter/twcs/twcs.csv')
str(tweets)
```

The data contains 2811774 observations with seven variables, including tweet IDs, author IDs, and timestamps.

## Data Processing

First, we will convert the `inbound` column to logical format so we can filter for inbound tweets more easily.

```{r}
# Convert the 'inbound' column to logical type
tweets$inbound <- tweets$inbound == "True"
```

## Identifying First Inbound Messages

Now, we filter the data to identify the first inbound customer messages that are not replies to previous tweets.

```{r}
# Pick only inbound tweets that aren't in reply to anything
first_inbound <- tweets %>%
  filter(is.na(in_response_to_tweet_id) & inbound)
cat("Found", nrow(first_inbound), "first inbound messages.\n")
```

## Merging Inbound Messages with Responses

We merge these first inbound messages with the rest of the dataset to capture company responses.

```{r}
# Merge in all tweets in response
inbounds_and_outbounds <- first_inbound %>%
  inner_join(tweets, by = c("tweet_id" = "in_response_to_tweet_id"))
cat("Found", nrow(inbounds_and_outbounds), "responses.\n")
```

## Filtering for Company Responses

Finally, we filter the merged data to keep only the responses from companies.

```{r}
# Filter out cases where reply tweet isn't from company
inbounds_and_outbounds <- inbounds_and_outbounds %>%
  filter(inbound.y == FALSE)

# Final output
cat("Found", nrow(inbounds_and_outbounds), "responses from companies.\n")
cat("Tweets Preview:\n")
print(head(inbounds_and_outbounds))
```

## Conclusion

This analysis identified the initial customer support requests and corresponding responses from companies on Twitter. The processed dataset provides insights into the nature of customer support interactions and can be used for further analysis, such as sentiment analysis or response time predictions.
